---
title: "Baseline Data: Demographics"
output: 
  html_document:
    toc: yes
    number_sections: no
    theme: spacelab
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
#loading necessary packages, functions, and data
source("/git_repositories/bangla/scripts/load_packages.R")
source("/git_repositories/bangla/scripts/plotting_functions.R")
baseline <- readRDS("~/Dropbox/Bangladesh Projects/Factories _ EWP/Data/baseline/in_process_data/cleaned_baseline.RDS")
```

#a note about this analysis
The numbers above bar plots are percentages. Any dotted lines on histograms are the mean for that variable. 

#basic demographics
##gender
Sex/Gender are nearly identical. 

```{r echo=FALSE, fig.width=2.5, fig.height=3.75, cache=TRUE}
plot_percent(baseline, "gender") #gender
plot_percent(baseline, "sex") #nearly identical
```

6% of people's gender was reported to be wrong. As a reference point, 7% of people's names and factory line, and 14% of people's salary amount were reported to be wrong.

```{r echo = FALSE, fig.width=2.5, fig.height=3.75, cache=TRUE}
plot_percent(baseline, "idconf_gender") #6% of people's gender was wrong
```

Of the 6%, more Males (previously labeled as females) correcting their gender. This may be indicative of [hijrahs](http://en.wikipedia.org/wiki/Hijra_%28South_Asia%29).

```{r, echo=FALSE, fig.width=2.5, fig.height=3.75, cache=TRUE}
plot_percent(baseline, "identer_gender")
#   table(baseline$idconf_name)#as a reference point, 7% of ppl's names wrong..
#   table(baseline$idconf_fline)#and factory line
#   table(baseline$idconf_salamount) #14% incorrect salary amount
```

##religion
No surprises here:
```{r, echo=FALSE, fig.width=2.5, fig.height=3.75, cache=TRUE}
plot_percent(baseline, "dreligion") #religion
```

#family status
##children
Does the respondent have children (left) and whether or not the children reside with the respondent (right). Children **overwhelmingly** not living with parent. 

```{r, echo=FALSE, fig.width=2.5, fig.height=3.75, cache=TRUE}
plot_percent(baseline, "dchild") #children
plot_percent(baseline, "dchild_stay") #do children live with you
```

##marital status
Marriage numbers (left) and marriage numbers by gender (right): 

```{r, echo=FALSE, fig.width=2.5, fig.height=3.75, cache=TRUE}
plot_percent(baseline, "dmarried") #marriage
```
```{r, echo=FALSE, fig.width=4, fig.height=3.75, cache=TRUE}
plot_percent2(baseline, "dmarried", "gender") #marriage rate by gender
```

60/40 split between those that live/don't live with their spouse:

```{r, echo=FALSE, fig.width=2.5, fig.height=3.75, cache=TRUE}
plot_percent(baseline, "dlive_sp") #live together with spouse 
```

##dependent family
Average of 4-5 dependent family members on respondent for both food (left) and income (right).

```{r, echo=FALSE, fig.width=2.5, fig.height=3.75, cache=TRUE}
plot_hist(baseline, "dmem_dep_food") #fam dependent on food
plot_hist(baseline, "dmem_dep_fin") #fam dependent on income
```

#credentials
##education
```{r, echo=FALSE, fig.width=11.5, fig.height=3, cache=TRUE}
plot_percent(baseline, "dedu", coordflippin = T) #education
```

Literacy in Bangla is 60/40 (left), however for English it's only 10/90 (right):

```{r, echo=FALSE, fig.width=2.5, fig.height=3.75, cache=TRUE}
plot_percent(baseline, "dletterb") #literacy in Bangla
plot_percent(baseline, "dlettere") #literacy in English
```

##work experience
Years at any factory (top) and years at current job (bottom):
```{r, echo=FALSE, fig.width=11.5, fig.height=3, cache=TRUE}
plot_percent(baseline, "dy_garment", coordflippin = T) #years at any garment factory 
plot_percent(baseline, "dy_currjob", coordflippin = T) #years at current job
```

Years intended to work in the future. Majority of respondents intend to work 1-6 years longer:

```{r, echo=FALSE, fig.width=11.5, fig.height=3, cache=TRUE}
plot_percent(baseline, "dy_exp", coordflippin = T) #how many more years intended to work
```

#income

Tri-modal salary spread:

```{r, echo=FALSE, fig.width=6, fig.height=3.5, warning=FALSE, cache=TRUE}
ggplot(baseline, aes(x=salamount)) + 
      geom_histogram(colour="black", fill = "#F0E442") + 
  geom_vline(aes(xintercept=mean(salamount, na.rm=T)),   
               color="black", linetype="dashed", size=.5)
```

A look at salary by gender (top), and by gender + marriage (bottom). Noteworthy that **no real difference on aggregate** for income, and that **married males make more than unmarried males**:

```{r, echo=FALSE, fig.width=12, fig.height=3, cache=TRUE}
ggplot(filter(baseline, !is.na(gender)), #income by gender
  aes(x=gender, y=salamount, fill=gender)) + geom_boxplot() + 
  guides(fill=FALSE) + coord_flip()

ggplot(filter(baseline, !is.na(gender)), #income + gender + marital status
  aes(x=gender, y=salamount, fill=dmarried)) + geom_boxplot() + coord_flip()
```

A look at spousal salary. Noteworthy that 23% of respondent spouses' do not have a salary:
```{r, echo=FALSE, fig.width=11.5, fig.height=3, cache=TRUE}
plot_percent(baseline, "dsp_inc", coordflippin = T) #spouse's income
```

##overtime
Overtime earnings overall (top) and by gender (bottom):
```{r, echo=FALSE, fig.width=12, fig.height=3, cache=TRUE}
plot_percent(baseline, "dinc_over", coordflippin = T) #monthly overtime earnings
plot_percent2(baseline, "dinc_over", "gender", coordflippin = T) #by gender
```

#10-step ladder
The following section has questions based on the 10 step ladder; the first being the worst and the tenth being the best. 

###communal respect
A quarter of respondents feel they have maximum street cred:
```{r, echo=FALSE, fig.width=11.5, fig.height=3, cache=TRUE}
plot_percent(baseline, "dresp_comm", coordflippin = T) #street cred/respect
```

###life: right now
Most feel like everything is in it's right place:
```{r, echo=FALSE, fig.width=11.5, fig.height=3, cache=TRUE}
plot_percent(baseline, "dcurr_status", coordflippin = T) #life right now
```

###life: in 5 years
Still most feel like things will get dramatically better:
```{r, echo=FALSE, fig.width=11.5, fig.height=3, cache=TRUE}
plot_percent(baseline, "dfut_status", coordflippin = T) #where you'll be in life in 5 years
```

###life: 5 years ago
And most feel things significantly improved:
```{r, echo=FALSE, fig.width=11.5, fig.height=3, cache=TRUE}
plot_percent(baseline, "dpast_status", coordflippin = T) #where you were in life 5 years ago  
```

#misc
##factory
```{r, echo=FALSE, fig.width=2.5, fig.height=3.75, cache=TRUE}
plot_percent(baseline, "factory") #factory
```

##advice
```{r, echo=FALSE, fig.width=2.5, fig.height=3.75, cache=TRUE}
plot_hist(baseline, "dadvice") #people come to you for advice
```


