---
title: "Baseline Data: Owned Assets"
date: "Updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: yes
    number_sections: no
    theme: spacelab
    self_contained: no
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
#loading necessary packages, functions, and data
source("/git_repositories/bangla/scripts/load_packages.R")
source("/git_repositories/bangla/scripts/plotting_functions.R")
baseline <- readRDS("~/Dropbox/Bangladesh Projects/Factories _ EWP/Data/baseline/in_process_data/cleaned_baseline.RDS")
```


Please tell me if  your household in Dhaka owns any of the following items:

#eletronics 

##radios
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_radio")
```
those that do have:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "asnradios")
```

##TVs
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_tv")
```
those that do have:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "asntv")
```

##video/DVD
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_video")
```

##mobile phones
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_mobile")
```
those that do have:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "asnmobile")
```

##computers
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_pc")
```
those that do have:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "asnpc")
```

\
[back to table of contents](#TOC)

#sewing machines                      
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_sewing")
```
those that do have:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "asnsewing")
```

#fans
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_fan")
```
those that do have:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "asnfan")
```

#kerosene lamps
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_keros")
```
those that do have:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "asnkerosene")
```

\
[back to table of contents](#TOC)


#cooking 

##stoves
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_stove")
```
those that do have:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "asnstove")
```

##pots
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_pot")
```
those that do have:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "asnpot")
```

##fridge
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_fridge")
```
those that do have:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "asnfridge")
```
\
[back to table of contents](#TOC)


#irons
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_iron")
```
those that do have:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "asniron")
```

#mosquito nets
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_net")
```
those that do have:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "asnnets")
```

#generator
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_gener")
```
those that do **(8)** have:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "asngenerator")
```

\
[back to table of contents](#TOC)


#transportation

##bike
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_bike")
```
those that do **(8)** have:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "asnbike")
```

##motorbikes

```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_motor")
```
those that do **(2)** have:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "asnmotor")
```

##other motor vehicles
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "ashas_otherm")
```
those that do **(2)** have:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "asnotherm")
```


