---
title: "Baseline Data: Consumption"
date: "Updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: yes
    number_sections: no
    theme: spacelab
    self_contained: no
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#loading necessary packages, functions, and data
source("/git_repositories/bangla/scripts/load_packages.R")
source("/git_repositories/bangla/scripts/plotting_functions.R")
baseline <- readRDS("~/Dropbox/Bangladesh Projects/Factories _ EWP/Data/baseline/in_process_data/cleaned_baseline.RDS")
```


```{r, echo=FALSE}
#creating NAs for relevant variables
baseline <- baseline %>%
    mutate(cper_inc_share = create_NA(cper_inc_share), blelse_food = create_NA(blelse_food),
           blelse_special = create_NA(blelse_special), blelse_saving = create_NA(blelse_saving),
           blelse_services = create_NA(blelse_services), blelse_other = create_NA(blelse_other))
           
#             = create_NA(), 
#             = create_NA(),           
#             = create_NA(), 
#             = create_NA(),           
```


#general consumption

do you feel obligated to turn over a part of your income to your spouse or another family member?

```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "cinc_share", coordflippin = F)
```

how much as a percentage do you turn over?
```{r, echo=FALSE, fig.width=11, fig.height=4, cache=FALSE, warning=FALSE}
plot_percent(baseline, "cper_inc_share", coordflippin = T)
```

does your spouse or other family member turn over part of his or her income to you?
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "cinc_from_sp", coordflippin = F)
```

who is responsible for budgeting the household income? 
```{r, echo=FALSE, fig.width=14, fig.height=4, cache=FALSE}
plot_percent(baseline, "cmem_budget", coordflippin = T)
```

in your household, who controls spending decisions for food and everyday expenses?
```{r, echo=FALSE, fig.width=14, fig.height=4, cache=FALSE}
plot_percent(baseline, "ccontr_food", coordflippin = T)
```

in your household, who controls spending decisions for special goods (sweets, meals out, movies, entertainment etc.)?
```{r, echo=FALSE, fig.width=14, fig.height=4, cache=FALSE}
plot_percent(baseline, "ccontr_special", coordflippin = T)
```

in your household, who controls spending decisions for larger purchases?
```{r, echo=FALSE, fig.width=14, fig.height=4, cache=FALSE}
plot_percent(baseline, "ccontr_large", coordflippin = T)
```


\
[back to table of contents](#TOC)

#consumption breakdown: percentage of income

##main expenses
thinking about the 5 days after you receive your salary, what part of your wage do you spend on the following items? 

payment of rent:
```{r, echo=FALSE, fig.width=5, fig.height=4, cache=FALSE}
plot_percent(baseline, "b5pay_rent")
```

payment of bills (electricity, water, phone, cable etc.):
```{r, echo=FALSE, fig.width=5, fig.height=4, cache=FALSE}
plot_percent(baseline, "b5pay_bills")
```

payment of school fees
```{r, echo=FALSE, fig.width=5, fig.height=4, cache=FALSE}
plot_percent(baseline, "b5pay_school")
```        

repayment of loans and interest
```{r, echo=FALSE, fig.width=5, fig.height=4, cache=FALSE}
plot_percent(baseline, "b5pay_loans")
```        

money given to spouse/household/family members in Dhaka
```{r, echo=FALSE, fig.width=5, fig.height=4, cache=FALSE}
plot_percent(baseline, "b5money_sporfam")
```        

money sent to family members in village home/place of origin
```{r, echo=FALSE, fig.width=5, fig.height=4, cache=FALSE}
plot_percent(baseline, "b5money_sent")
```        

money left for spending on everything else
```{r, echo=FALSE, fig.width=5, fig.height=4, cache=FALSE}
plot_percent(baseline, "b5money_else")
```        


\
[back to table of contents](#TOC)

##income leftover

thinking of the part of your wage that is left over for spending on everything else, how do you allocate this amount between the following items? 

on food
```{r, echo=FALSE, fig.width=5, fig.height=4, cache=FALSE}
plot_percent(baseline, "blelse_food")
```

special goods (mobile phone credit, entertainment, movies, books etc.) for yourself
```{r, echo=FALSE, fig.width=5, fig.height=4, cache=FALSE}
plot_percent(baseline, "blelse_special")
```

savings
```{r, echo=FALSE, fig.width=5, fig.height=4, cache=FALSE}
plot_percent(baseline, "blelse_saving")
```
      
spending on services (healthcare, haircuts,etc.)      
```{r, echo=FALSE, fig.width=5, fig.height=4, cache=FALSE}
plot_percent(baseline, "blelse_services") 
```

other
```{r, echo=FALSE, fig.width=5, fig.height=4, cache=FALSE}
plot_percent(baseline, "blelse_other")
```
   
   
\
[back to table of contents](#TOC)

#consumption breakdown: actual amounts
how much does your household spend on an average month on the following items? please enter amounts:

##rent

```{r, echo=FALSE, fig.width=3.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "hhehhpay_rent")
```

```{r, results='asis', echo=FALSE}
stargazer(select(baseline,hhehhpay_rent), type = "html", flip=T)
```

##bills 
electricity, water, phone, cable etc.

```{r, echo=FALSE, fig.width=3.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "hhehhpay_bills")
```

```{r, results='asis', echo=FALSE}
stargazer(select(baseline,hhehhpay_bills), type = "html", flip=T)
```

##school fees

```{r, echo=FALSE, fig.width=3.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "hhehhpay_school")
```

```{r, results='asis', echo=FALSE}
stargazer(select(baseline,hhehhpay_school), type = "html", flip=T)
```

##repayment of loans and interest

```{r, echo=FALSE, fig.width=3.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "hhehhpay_loans")
```

```{r, results='asis', echo=FALSE}
stargazer(select(baseline,hhehhpay_loans), type = "html", flip=T)
```
    
##money given to family members in Dhaka

```{r, results='asis', echo=FALSE}
stargazer(select(baseline,hhehhmoney_fam), type = "html", flip=T)
```

##money sent to family members in village home/place of origin

```{r, echo=FALSE, fig.width=3.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "hhehhmoney_sent")
```

```{r, results='asis', echo=FALSE}
stargazer(select(baseline,hhehhmoney_sent), type = "html", flip=T)
```

##food    

```{r, echo=FALSE, fig.width=3.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "hhehh_food")
```

```{r, results='asis', echo=FALSE}
stargazer(select(baseline,hhehh_food), type = "html", flip=T)
```

##special goods
mobile phone credit, entertainment, movies, books etc.

```{r, echo=FALSE, fig.width=3.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "hhehh_special")
```

```{r, results='asis', echo=FALSE}
stargazer(select(baseline,hhehh_special), type = "html", flip=T)
```

##savings

```{r, echo=FALSE, fig.width=3.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "hhehh_saving")
```

```{r, results='asis', echo=FALSE}
stargazer(select(baseline,hhehh_saving), type = "html", flip=T)
```

##services
healthcare, haircuts, etc.

```{r, echo=FALSE, fig.width=3.5, fig.height=4, cache=FALSE}
plot_hist(baseline, "hhehh_services")
```

```{r, results='asis', echo=FALSE}
stargazer(select(baseline,hhehh_services), type = "html", flip=T)
```
   
##other

```{r, results='asis', echo=FALSE}
stargazer(select(baseline,hhehh_other), type = "html", flip=T)
```


\
[back to table of contents](#TOC)

#consumption priorities

##biggest expense
in the last 2 years, what was the single biggest expense you have had to make at one time?
```{r, echo=FALSE, fig.width=13, fig.height=5, cache=FALSE}
plot_percent(baseline, "c_prbig_exp", coordflippin = T)
```

amount:
```{r, echo=FALSE, fig.width=13, fig.height=5, cache=FALSE}
plot_percent(baseline, "c_pram_big_exp", coordflippin = T)
table(baseline$c_pram_big_exp, useNA = 'ifany')
```

##biggest withdrawl

what is the biggest withdrawal from your savings/money put away that you have made at one time over the last 2 years?
```{r, echo=FALSE, fig.width=13, fig.height=4, cache=FALSE}
plot_percent(baseline, "c_prbig_withdr", coordflippin = T)
```

amount:
```{r, echo=FALSE, fig.width=13, fig.height=3.75, cache=FALSE}
plot_percent(baseline, "c_pram_big_withdr", coordflippin = T)
table(baseline$c_pram_big_withdr, useNA = 'ifany')
```

##hypothetical
if you were given 15,000 Taka today, for what purposes would you use this money?

```{r}
# yo <- melt(baseline, id=c("resp_id", "c_pr2given_money1","c_pr2given_money2", "c_pr2given_money3"))

table(baseline$c_pr2given_money1, useNA = 'ifany')
table(baseline$c_pr2given_money2, useNA = 'ifany')
table(baseline$c_pr2given_money3, useNA = 'ifany')
```

\
[back to table of contents](#TOC)

