
---
title: "Baseline Data: Credit"
date: "Updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: yes
    number_sections: no
    theme: spacelab
    self_contained: no
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
#loading necessary packages, functions, and data
source("/git_repositories/bangla/scripts/load_packages.R")
source("/git_repositories/bangla/scripts/plotting_functions.R")
baseline <- readRDS("~/Dropbox/Bangladesh Projects/Factories _ EWP/Data/baseline/in_process_data/cleaned_baseline.RDS")
```


 

#credit
"crhas_loans"          "crtot_loans"          "crcurram_loan"       
"cragree_sp_loans"     "lloans_out1"          "lloans_out2"          "lloans_out3"         
"lloans_out4"          "lrep_l_count"         "loan_type_out1"       "nfe_loan1"           
"purp_loan1"           "plan_exp_loan1"       "amount_loan1"         "recipient_loan1"     
"repay_loan1"          "num_paym_loan1"       "n_paym_left_loan1"    "freq_paym_loan1"     
"size_paym_loan1"      "loan_jointly1"        "loan_type_out2"       "nfe_loan2"           
"purp_loan2"           "plan_exp_loan2"       "amount_loan2"         "recipient_loan2"     
"repay_loan2"          "num_paym_loan2"       "n_paym_left_loan2"    "freq_paym_loan2"     
"size_paym_loan2"      "loan_jointly2"        "loan_type_out3"       "nfe_loan3"           
"purp_loan3"           "plan_exp_loan3"       "amount_loan3"         "recipient_loan3"     
"repay_loan3"          "num_paym_loan3"       "n_paym_left_loan3"    "freq_paym_loan3"     
"size_paym_loan3"      "loan_jointly3"        "loan_type_out4"       "nfe_loan4"           
"purp_loan4"           "plan_exp_loan4"       "amount_loan4"         "recipient_loan4"     
"repay_loan4"          "num_paym_loan4"       "n_paym_left_loan4"    "freq_paym_loan4"     
"size_paym_loan4"      "loan_jointly4"        "in_lloan_ref1"        "in_lloan_ref2"       
"in_lloan_ref3"        "in_lloan_ref4"        "in_lloan_ref5"        "in_lworry_repay"     
"in_ln_loans_plan"     "in_lam_plan"          "in_lpurp_plan"        "in_lrecip_plan"      
 "in_lsalary_adv"       "in_lfreq_sal_adv"     "in_ladv_purp"   



```{r, echo=FALSE, fig.width=14, fig.height=4, cache=TRUE}
plot_percent(baseline, "fcapborr_end", coordflippin = T)
```



```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=TRUE}
plot_percent(baseline, "fcapcut_meals", coordflippin = F)
```


\
[back to table of contents](#TOC)