
---
title: "Baseline Data: Remittances"
date: "Updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: yes
    number_sections: no
    theme: spacelab
    self_contained: no
---

```{r, echo=FALSE, warning=FALSE, message=FALSE}
#loading necessary packages, functions, and data
source("/git_repositories/bangla/scripts/load_packages.R")
source("/git_repositories/bangla/scripts/plotting_functions.R")
baseline <- readRDS("~/Dropbox/Bangladesh Projects/Factories _ EWP/Data/baseline/in_process_data/cleaned_baseline.RDS")
```



#remittances
"r_srem_s_past6"       "r_srem_am_s_past6"    "r_sn_recipients"      "r_sn_receipients"    
"r_sr_s_rep_count"     "num_mem_s1"           "mem_s_name1"          "mem_s_age1"          
"mem_s_residence1"     "s_num_transfpast6_1"  "s_size_transfpast6_1" "s_way_transfpast6_1" 
"s_num_receipast6_1"   "s_size_receipast6_1"  "s_way_receipast6_1"   "s_num_next9_1"       
"s_size_next9_1"       "s_num_recnext9_1"     "s_size_recnext9_1"    "num_mem_s2"          
"mem_s_name2"          "mem_s_age2"           "mem_s_residence2"     "s_num_transfpast6_2" 
"s_size_transfpast6_2" "s_way_transfpast6_2"  "s_num_receipast6_2"   "s_size_receipast6_2" 
"s_way_receipast6_2"   "s_num_next9_2"        "s_size_next9_2"       "s_num_recnext9_2"    
"s_size_recnext9_2"    "num_mem_s3"           "mem_s_name3"          "mem_s_age3"          
"mem_s_residence3"     "s_num_transfpast6_3"  "s_size_transfpast6_3" "s_way_transfpast6_3" 
"s_num_receipast6_3"   "s_size_receipast6_3"  "s_way_receipast6_3"   "s_num_next9_3"       
"s_size_next9_3"       "s_num_recnext9_3"     "s_size_recnext9_3"    "num_mem_s4"          
"mem_s_name4"          "mem_s_age4"           "mem_s_residence4"     "s_num_transfpast6_4" 
"s_size_transfpast6_4" "s_way_transfpast6_4"  "s_num_receipast6_4"   "s_size_receipast6_4" 
"s_way_receipast6_4"   "s_num_next9_4"        "s_size_next9_4"       "s_num_recnext9_4"    
"s_size_recnext9_4"    "num_mem_s5"           "mem_s_name5"          "mem_s_age5"          
"mem_s_residence5"     "s_num_transfpast6_5"  "s_size_transfpast6_5" "s_way_transfpast6_5" 
"s_num_receipast6_5"   "s_size_receipast6_5"  "s_way_receipast6_5"   "s_num_next9_5"       
"s_size_next9_5"       "s_num_recnext9_5"     "s_size_recnext9_5"    "num_mem_s6"          
"mem_s_name6"          "mem_s_age6"           "mem_s_residence6"     "s_num_transfpast6_6" 
"s_size_transfpast6_6" "s_way_transfpast6_6"  "s_num_receipast6_6"   "s_size_receipast6_6" 
"s_way_receipast6_6"   "s_num_next9_6"        "s_size_next9_6"       "s_num_recnext9_6"    
"s_size_recnext9_6"    "num_mem_s7"           "mem_s_name7"          "mem_s_age7"          
"mem_s_residence7"     "s_num_transfpast6_7"  "s_size_transfpast6_7" "s_way_transfpast6_7" 
"s_num_receipast6_7"   "s_size_receipast6_7"  "s_way_receipast6_7"   "s_num_next9_7"       
"s_size_next9_7"       "s_num_recnext9_7"     "s_size_recnext9_7"    "r_rrem_r_past6"      
"r_rrem_am_r_past6"    "r_rn_senders"         "r_rr_r_rep_count"     "num_mem_r1"          
"ment_rost1_1"         "mem_r_name1"          "mem_r_age1"           "mem_r_residence1"    
"r_num_receipast6_1"   "r_size_receipast6_1"  "r_way_receipast6_1"   "r_num_transfpast6_1" 
"r_size_transfpast6_1" "r_way_transfpast6_1"  "r_num_next9_1"        "r_size_next9_1"      
"r_num_recnext9_1"     "r_size_recnext9_1"    "num_mem_r2"           "ment_rost1_2"        
"mem_r_name2"          "mem_r_age2"           "mem_r_residence2"     "r_num_receipast6_2"  
"r_size_receipast6_2"  "r_way_receipast6_2"   "r_num_transfpast6_2"  "r_size_transfpast6_2"
"r_way_transfpast6_2"  "r_num_next9_2"        "r_size_next9_2"       "r_num_recnext9_2"    
"r_size_recnext9_2"    "num_mem_r3"           "ment_rost1_3"         "mem_r_name3"         
"mem_r_age3"           "mem_r_residence3"     "r_num_receipast6_3"   "r_size_receipast6_3" 
"r_way_receipast6_3"   "r_num_transfpast6_3"  "r_size_transfpast6_3" "r_way_transfpast6_3" 
"r_num_next9_3"        "r_size_next9_3"       "r_num_recnext9_3"     "r_size_recnext9_3"   
"num_mem_r4"           "ment_rost1_4"         "mem_r_name4"          "mem_r_age4"          
"mem_r_residence4"     "r_num_receipast6_4"   "r_size_receipast6_4"  "r_way_receipast6_4"  
"r_num_transfpast6_4"  "r_size_transfpast6_4" "r_way_transfpast6_4"  "r_num_next9_4"       
"r_size_next9_4"       "r_num_recnext9_4"     "r_size_recnext9_4"    "num_mem_r5"          
"ment_rost1_5"         "mem_r_name5"          "mem_r_age5"           "mem_r_residence5"    
"r_num_receipast6_5"   "r_size_receipast6_5"  "r_way_receipast6_5"   "r_num_transfpast6_5" 
"r_size_transfpast6_5" "r_way_transfpast6_5"  "r_num_next9_5"        "r_size_next9_5"      
"r_num_recnext9_5"     "r_size_recnext9_5"    "ever_trans_mob"       "ever_recei_mob"      
"remit_tools1"         "remit_tools2"         "remit_tools3"         "remit_tools4"        
"remit_tools5"         "remit_tools6"         




```{r, echo=FALSE, fig.width=14, fig.height=4, cache=FALSE}
plot_percent(baseline, "fcapborr_end", coordflippin = T)
```



```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(baseline, "fcapcut_meals", coordflippin = F)
```


\
[back to table of contents](#TOC)