
---
title: "Baseline Data: Psych Measures"
date: "Updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: yes
    number_sections: no
    theme: spacelab
    self_contained: no
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
#loading necessary packages, functions, and data
source("/git_repositories/bangla/scripts/load_packages.R")
source("/git_repositories/bangla/scripts/plotting_functions.R")
baseline <- readRDS("~/Dropbox/Bangladesh Projects/Factories _ EWP/Data/baseline/in_process_data/cleaned_baseline.RDS")
```

#risk + time preferences
"r_prrisk_fin"         "r_prrisk_all"        
"r_prlottery1"         "r_prlottery2"         "r_prlottery3"         "r_prlottery4"        
"r_prlottery5"         "r_prlottery6"         "t_prtime_pref1"       "t_prtime_pref2"      
"t_prtime_pref3"       "t_prtime_pref4"       "t_prtime_pref5"       "t_prtime_pref6"      
"t_prpatience"         
#trust and altruism
"trualtr_500"          "trutrust1"            "trutrust2"           
"trutrust3"            
#locus of control
"locprobl"            
"locmisf"              "loccontr"             "locluck"              "locmanage"           
#work satisfaction
"wsoverall_sat"        "wswage_sat"           "wscond_sat"           "wsbenefits_sat"      
"wsrecommend"          "metainstanceID" 



```{r, echo=FALSE, fig.width=14, fig.height=4, cache=TRUE}
plot_percent(baseline, "fcapborr_end", coordflippin = T)
```



```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=TRUE}
plot_percent(baseline, "fcapcut_meals", coordflippin = F)
```


\
[back to table of contents](#TOC)