---
title: "Follow-up 1 Data: Demographics"
date: "Updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: yes
    number_sections: no
    theme: spacelab
    self_contained: no
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
#loading necessary packages, functions, and data
source("/git_repositories/bangla/scripts/load_packages.R")
source("/git_repositories/bangla/scripts/plotting_functions.R")
followup <- readRDS("~/Dropbox/Bangladesh Projects/Factories _ EWP/Data/follow-up 1/in_process_data/cleaned_followup1.RDS")
```

#means and SDs
for numeric variables
```{r, echo=FALSE}
followup_mSD <- select(followup, 
            children = dchild_n, child_D = dchild_D)
```

```{r, results='asis', echo=FALSE}
stargazer(followup_mSD, type="html", flip = F)
```

\
[back to table of contents](#TOC)

#basic demographics
##gender

```{r echo=FALSE, fig.width=2.5, fig.height=4, cache=TRUE}
plot_percent(followup, "gender")
```

11% of respondents' gender was reported to be wrong. As a reference point, 17% of people's names and factory line were reported to be wrong:

```{r echo = FALSE, fig.width=2.5, fig.height=4, cache=TRUE}
plot_percent(followup, "idconf_gender")
```

Of the 11%, more Females (previously labeled as males) correcting their gender. Interesting that this was the opposite in the baseline. 

```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=TRUE}
plot_percent(followup, "identer_gender")
```


#family status

##mariage
7 in 10 are married: 
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=TRUE}
plot_percent(followup, "dmarried") 
```

Of the unmarried, most never were: 
```{r, echo=FALSE, fig.width=11, fig.height=2.75, cache=T}
plot_percent(followup, "dot_marr", coordflippin = T)
```     

If married, 35% of people have spouse that works in same factory:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=TRUE}
plot_percent(followup, "dsp_garm") 
```

##children

7/10 of respondents have kids, 1.5 on average:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=T}
plot_percent(followup, "dchild") 
plot_hist(followup, "dchild_n")
```

Noteworthy that not as many children living with parent in Dhaka:
```{r, echo=FALSE, fig.width=6, fig.height=3.5, warning=FALSE, cache=TRUE}
plot_hist(followup, "dchild_D")
```

\
[back to table of contents](#TOC)


#income

**We only have 44 respondents for income!** 

```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=TRUE}
plot_percent(followup, "am_inc1", coordflippin = T) 
```

Only **2 percent of people have any income from another source** in past 30 days:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=TRUE}
plot_percent(followup, "iot_income")
```

Of those 2 percent, main source is subletting:
```{r, echo=FALSE, fig.width=13, fig.height=3, cache=TRUE}
plot_percent(followup, "iwhat_inc1", coordflippin = T) 
```

\
[back to table of contents](#TOC)

```{r, eval=FALSE}
#sugested variables to keep:
"factory"             
"gender"
"dmarried"            
"dot_marr"
"dsp_garm"
"dchild"               
"dchild_n"            
"dchild_D"   
"iot_income"   
```

\
[back to table of contents](#TOC)


