---
title: "Follow-up 1 Data: Consumption"
date: "Updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: yes
    number_sections: no
    theme: spacelab
    self_contained: no
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
#loading necessary packages, functions, and data
source("/git_repositories/bangla/scripts/load_packages.R")
source("/git_repositories/bangla/scripts/plotting_functions.R")
followup <- readRDS("~/Dropbox/Bangladesh Projects/Factories _ EWP/Data/follow_up/in_process_data/cleaned_followup.RDS")
```

#food consumption

Most spend between 1-2K monthly on rice (top) and meat (bottom):
```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "fcrice", coordflippin = T) 
```

```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "fcmeat", coordflippin = T) 
```

Sugar, tea and coffee, other food and drink consumed outside the house, special goods such as sweets, packaged snacks, soft drinks etc:
```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "fcspice", coordflippin = T) 
```

**Most eat fish/meat more than once a day** (original question was how many times in last 30 days?):

```{r, echo=FALSE, fig.width=7, fig.height=4, cache=FALSE}
plot_hist(followup, "fctimes_meat")
```

\
[back to table of contents](#TOC)

#non-food consumption

##rent
**Most spend as much as they do on rice as they do on rent**:
```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "nf_consrent", coordflippin = T) 
```

Noteworthy that **women spend more in nearly each tranche than do men**:
```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent2(followup, "nf_consrent", "gender", coordflippin = T)
```

##transportation/communication

Transportation costs for work:
```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "nf_constrans_w", coordflippin = T) 
```

to visit family/friends: 
```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "nf_constrans_fam", coordflippin = T) 
```

phone expenses:
```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "nf_consphone", coordflippin = T) 
```

##education

```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "nf_consedu", coordflippin = T) 
```

##health

```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "nf_conshealth", coordflippin = T) 
```

##entertainment

very few respondents spent much, if anything, on non-festival related gifts:
```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "nf_consgifts", coordflippin = T) 
```

likewise on non-festival related entertainment (anything music, meals outside at restaurant, cinema, books etc):
```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "nf_consentertain", coordflippin = T) 
```

increase in spending for ceremonies and festivals:
```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "nf_consfestiv", coordflippin = T) 
```

##misc

Seems like a very broad category! Clothes, shoes, jeweley, cosmetics, soap, toiletry products etc.:
```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "nf_consclothes", coordflippin = T) 
```

Apart from all of the above, **only 8% of respondents made any purchases that cost more than 1000 Thaka in the last month**:
```{r, echo=FALSE, fig.width=2.5, fig.height=4, cache=FALSE}
plot_percent(followup, "durmore_1000")
```

of those 8%, those purchases fell under:
```{r, echo=FALSE, fig.width=15, fig.height=5, warning=FALSE, cache=FALSE}
plot_percent(followup, "durdurables1", coordflippin = T)
```

\
[back to table of contents](#TOC)

```{r, eval=FALSE}    
#sugested variables to keep:
"fcrice"
"fcmeat"
"fcspice"
"fctimes_meat"
"nf_consrent"
"nf_constrans_w"
"nf_constrans_fam"
"nf_consphone"          
"nf_consedu"           
"nf_conshealth"         
"nf_consgifts"          
"nf_consentertain"
"nf_consfestiv"         
"nf_consclothes"  
"durmore_1000"         
"durdurables1" 
```


\
[back to table of contents](#TOC)



