---
title: "Follow-up 1 Data: Savings"
date: "Updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: yes
    number_sections: no
    theme: spacelab
    self_contained: no
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
#loading necessary packages, functions, and data
source("/git_repositories/bangla/scripts/load_packages.R")
source("/git_repositories/bangla/scripts/plotting_functions.R")
followup <- readRDS("~/Dropbox/Bangladesh Projects/Factories _ EWP/Data/follow_up/in_process_data/cleaned_followup.RDS")
```

#means and SDs
for numeric variables
```{r, echo=FALSE}
cheddar <- select(followup, sgam_sav1:sgam_sav17) %>% 
            transmute(overall_savings = rowSums(., na.rm = T))
```

```{r, results='asis', echo=FALSE}
stargazer(cheddar, type="html", flip = T)
```

\
[back to table of contents](#TOC)

#overall savings

more than half of people do no have any savings (top) and even less their spouses (bottom):
```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "sgrange_sav", coordflippin = T)
plot_percent(followup, "sgam_sav_sp", coordflippin = T)
```

large right skew of savings distribution, with **17K being the average**:
```{r, echo=FALSE, fig.width=7, fig.height=4, cache=FALSE}
ggplot(cheddar, aes(x=overall_savings)) + 
      geom_histogram(colour="black", fill = "#F0E442", binwidth = 100000) + 
  geom_vline(aes(xintercept=mean(overall_savings, na.rm=T)),   
               color="black", linetype="dashed", size=.5)
```

\
[back to table of contents](#TOC)


#ladder
How good do you feel at saving? For the actual savings figures, we see some optimism/hopefulness from respondents (Step 1 is really bad Step 10 is excellent)
```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "sgachi_goal_gen", coordflippin = T)
```

\
[back to table of contents](#TOC)

#formal savings
Do you have savings set aside in any of the following account (in your name, in your children's name or jointly in  your name and somebody else's name)? **Most choose DPS accounts**
```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "nfe_for1", coordflippin = T)
```

of the **529 respondents with formal accounts**, here is the breakdown of balances:
```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "bal_for_acc1", coordflippin = T)
```

Informal savings accounts: 
```{r, echo=FALSE, fig.width=17, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "nfe_info1", coordflippin = T)
```

of the **395 respondents with informal accounts**, here is breakdown of balances: 
```{r, echo=FALSE, fig.width=13, fig.height=3, warning=FALSE, cache=FALSE}
plot_percent(followup, "balance_info_acc1", coordflippin = T)
```


\
[back to table of contents](#TOC)


```{r, eval=FALSE}    
#sugested variables to keep:
"sgrange_sav"   
"sgam_sav_sp"   
"sgam_sav1":"sgam_sav17"
"sgachi_goal_gen"       
"nfe_for1"            
"bal_for_acc1"
"nfe_info1"             
"balance_info_acc1"     

#note it is not worth asking about second formal/informal accounts...
#we are only getting literally a handful of respondents mention anything

```


\
[back to table of contents](#TOC)




