---
title: "Follow-up 1 Data: Loans + Remittances"
date: "Updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: yes
    number_sections: no
    theme: spacelab
    self_contained: no
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
#loading necessary packages, functions, and data
source("/git_repositories/bangla/scripts/load_packages.R")
source("/git_repositories/bangla/scripts/plotting_functions.R")
followup <- readRDS("~/Dropbox/Bangladesh Projects/Factories _ EWP/Data/follow-up 1/in_process_data/cleaned_followup1.RDS")
```

#means and SDs
for numeric variables
```{r, echo=FALSE}
followup_mSD <- select(followup, rem_sentn_receipients)
```

```{r, results='asis', echo=FALSE}
stargazer(followup_mSD, type="html", flip = T)
```

#loans 

##number
**Over 1/2 respondents do not have any loans**:
```{r}
plot_percent(followup, "l_outlo_rep_count")
```

\
[back to table of contents](#TOC)

##source
Most loans are taken from family/friends. The first loan (top) and second loan (bottom):
```{r}
plot_percent(followup, "nfe_loan_out1", coordflippin = T)
```

```{r}
plot_percent(followup, "nfe_loan_out2", coordflippin = T)
```

\
[back to table of contents](#TOC)

##repayment
What is left for repayment on first loan is mostly to the tune of 1-3K Taka:
```{r}
plot_percent(followup, "am_loan_out1", coordflippin = T)
```

3/4 of respondents with second loans have below 3K Taka to pay back:
```{r}
plot_percent(followup, "am_loan_out2", coordflippin = T)
```

\
[back to table of contents](#TOC)

#remittances

**3/4 of respondents have sent money to friends/family** over the last month who do not live in household:
```{r}
plot_percent(followup, "rem_sentrem_s")
```

##number

The number of people over the past month:
```{r, echo=FALSE, fig.width=7, fig.height=4, cache=TRUE}
plot_hist(followup, "rem_sentn_receipients")
```

##amount

Total amount sent over past month for **most is between 2-5K Taka**:
```{r}
plot_percent(followup, "rem_senttot_am_s", coordflippin = T)
```

##to other members of household

Most respondents have not transfered moneys to another member of the same household:
```{r}
plot_percent(followup, "rem_senthhtr_s")
```

Of the **14% that have**, here is the breakdown of amount: 
```{r}
plot_percent(followup, "rem_sentam_hhtr_s", coordflippin = T)
```

\
[back to table of contents](#TOC)

```{r}
#sugested variables to keep:
"l_outlo_rep_count"
"nfe_loan_out1"        
"am_loan_out1"               
"nfe_loan_out2"
"am_loan_out2"          
"rem_sentrem_s"         
"rem_sentn_receipients"
"rem_senttot_am_s"     
"rem_senthhtr_s"       
"rem_sentam_hhtr_s"
```

\
[back to table of contents](#TOC)


