---
title: "Phone Follow Up Data: Standard"
date: "Updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: yes
    number_sections: no
    theme: spacelab
    self_contained: no
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
#loading necessary packages, functions, and data
source("/git_repositories/bangla/scripts/load_packages.R")
source("/git_repositories/bangla/scripts/plotting_functions.R")
phone <- readRDS("~/Dropbox/Bangladesh Projects/Factories _ EWP/Data/phone follow up/Phone_Fup_clean_08-11-15.RDS")
follow_up <- readRDS("~/Dropbox/Bangladesh Projects/Factories _ EWP/Data/follow_up/in_process_data/cleaned_followup.RDS")

```

```{r, echo=FALSE}
#for tranches
mess_range <- c("none", "I live in a mess and pay for food with rent", "Don't know", "less than 500 Taka", 
                "between 500 and 1000 Taka", "between 1000 and 2000 Taka", "between 2000 and 3000 Taka", 
                "Between 3000 and 5000 Taka", "Between 5000  and 8000 Taka", "Between 8000  and 10000 Taka", 
                "Between 10000 and 15000 Taka", "Between 15000 and 20000 Taka", "Between 25000  and 30000 taka", 
                "between 30000 and 35000 taka", "between 35000 and 40000 taka", "between 40000 and 45000 taka", 
                "between 45000 and 50000 taka", "more than 50000")
exp_range <- c("none", "Don't know", "less than 500 Taka", "between 500 and 1000 Taka", 
               "between 1000 and 2000 Taka", "between 2000 and 3000 Taka", "Between 3000 and 5000 Taka",
               "Between 5000  and 8000 Taka", "Between 8000  and 10000 Taka", "Between 10000 and 15000 Taka", 
               "Between 15000 and 20000 Taka", "Between 20000  and 25000 taka", "Between 25000  and 30000 taka",
               "between 30000 and 35000 taka", "between 35000 and 40000 taka", "between 40000 and 45000 taka",
               "between 45000 and 50000 taka", "more than 50000")
sav_range <- c("Refused to answer", "Don't know", "None", "Less than 3000 Taka", "Between 3000 and 5000 Taka", 
               "Between 5000  and 8000 Taka", "Between 8000  and 10000 Taka", "Between 10000 and 15000 Taka",
               "Between 15000 and 20000 Taka","Between 20000  and 25000 taka", "Between 25000  and 30000 taka",
               "between 30000 and 35000 taka", "between 35000 and 40000 taka", "between 40000 and 45000 taka",
               "between 45000 and 50000 taka", "between 50000 and 70000 taka", "between 70000 and 90000 taka",
               "between 90000 and 120000 taka", "between 120000 and 150000 taka", "more than 150000 taka")
acc_bal <- c("Refused to answer", "Don’t know", "no money", "Less than 2500 Taka",
             "Between 2500 and 5000 Taka", "Between 5000 and 10000 Taka", "Between 10000 and 15000 Taka",
             "Between 15000 and 20000 Taka", "Between 20000 and 30000 Taka", "Between 30000 and 50000 Taka",
             "between 50000 and 70000 taka", "between 70000 and 90000 taka", " between 90000 and 120000 taka",
             "between 120000 and 150000 taka", "more than 150000 taka")
loan_range <- c("Less than 500 Taka", "Between 500 and 1000 Taka",  "Between 1000 and 3000 Taka",
                "Between 3000 and 5000 Taka", "Between 5000 and 10000 Taka",
                "Between 10000 and 20000 Taka", "Between 20000 and 35000 taka",
                "Between 35000 and 50000 Taka", "between 50000 and 70000 taka",
                "between 70000 and 90000 taka", "between 90000 and 120000 taka", 
                "between 120000 and 150000 taka", "more than 150000 taka", "Don't know")
rem_range <- c("less than 500 Taka", "between 500 and 800 Taka", "between 800 and 1000 Taka",
               "between 1000 and 2000 Taka", "between 2000 and 5000 Taka",
               "between 5000 and 8000 Taka", "between 8000 and 10000 Taka",
               "between 10000 and 15000 Taka", "between 15000 and 20000 Taka",
               "between 20000 and 25000 Taka", "between 25000 and 30000 Taka",
               "more than 30000", "Don't know")
```

####NOTE: the numbers on top of the bars in plots represent percentages

#Food Consumption

> how much you have spent from your income on basic food items for yourself or others over the past 30 days:

####Rice, Lentils, pulses, cereals, Edible oils, Spices
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "fcrice", coordflippin = T) + scale_x_discrete(limits = mess_range)
#table(phone$fcrice, useNA = 'ifany')
```


####Meat and fish, Milk, butter, eggs, paneer, ghee, Fruit and vegetables
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "fcmeat", coordflippin = T) + scale_x_discrete(limits = mess_range)
```


####Tea, coffee, Sugar, Other food and drink consumed outside the house, Special goods such as sweets, packaged snacks, soft drinks
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "fcspice", coordflippin = T) + scale_x_discrete(limits = exp_range)
```


####How many times did you eat meat or fish in the last 30 days?
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_hist(phone, "fctimes_meat")
summary(phone$fctimes_meat)
```

####How many times did you skip a meal for not having enough money in the last 30 days?
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_hist(phone, "fcmeals_skip") + scale_x_discrete(limits = c(1:7))
summary(phone$fcmeals_skip)
```

\
[back to table of contents](#TOC)




#Non-Food Consumption

> How much did you spend from your income in total for yourself and others on the following items over the past 30 days?

####Rent and utilities  (individual or + spouse or other family in hh)
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "nf_consrent", coordflippin = T) + scale_x_discrete(limits = exp_range)
```

####Transportation
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "nf_constrans_all", coordflippin = T) + scale_x_discrete(limits = exp_range)
```

####Phone Credit
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "nf_consphone", coordflippin = T) + scale_x_discrete(limits = exp_range)
```

####School fees, uniforms, or other educational expenses
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "nf_consedu", coordflippin = T) + scale_x_discrete(limits = exp_range)
```

####Health care expenses: doctors, vaccines, medicines, hospital visits, haircuts
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "nf_conshealth", coordflippin = T) + scale_x_discrete(limits = exp_range)
```

####(non festive) Clothes, shoes, jeweley, Cosmetics, soap, toiletry products 
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "nf_consclothes", coordflippin = T) + scale_x_discrete(limits = exp_range)
```

####Ceremonies and festivals
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "nf_consfestiv", coordflippin = T) + scale_x_discrete(limits = exp_range)
```

####Other than what you have already mentioned, did you make any purchases that cost more than 1000 taka in the past 30 days?
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "durmore_1000", coordflippin = T)
```

####What have you purchased in the past 30 days that cost more than 1000 taka?
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "durdurables1", coordflippin = T)
```
  
  + NAs?
```{r, echo=FALSE}
table(is.na(phone$durdurables1))
```

\
[back to table of contents](#TOC)





#Savings

####How much savings do you currently have? Please include all savings and money set away in formal accounts, informal accounts, money saved in your name or together with spouse/other family members or friends in Dhaka or your place of origin.
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "sgrange_sav", coordflippin = T) + scale_x_discrete(limits = sav_range)
```


####Please enter exact amount of all savings set away in formal accounts, informal accounts, money saved in your name or together with spouse/other family members or friends in Dhaka or your place of origin.
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_hist(phone, "sgam_sav", mean = T, bin1 = F)
summary(phone$sgam_sav)
```

##formal savings

####Number of Formal Savings account:
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_hist(phone, "fsrep_f_count", mean = T, bin1 = T)
summary(phone$fsrep_f_count)
```

####Do you have savings set aside in any of the following accounts (in your name, in your children's name or jointly in your name and somebody else's name)? 
> account 1

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "nfe_for1", coordflippin = T) 
#table(phone$nfe_for1, useNA = "ifany")
```
   
   + NA's?
```{r, echo=FALSE}
table(is.na(phone$nfe_for1))
```

> account 2

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "nfe_for2", coordflippin = T) 
```
  
  + NA's?
```{r, echo=FALSE}
table(is.na(phone$nfe_for2))
```

####What is your current balance?
> account 1

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "bal_for_acc1", coordflippin = T) + scale_x_discrete(limits = acc_bal)
```
   
   + NA's?
```{r, echo=FALSE}
table(is.na(phone$bal_for_acc1))
```

> account 2

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "bal_for_acc2", coordflippin = T) + scale_x_discrete(limits = acc_bal)
```
  
  + NA's?
```{r, echo=FALSE}
table(is.na(phone$bal_for_acc2))
```

##informal savings

####Number of Informal Savings account:
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_hist(phone, "isrep_i_count", mean = T, bin1 = T)
summary(phone$fsrep_f_count)
```

####Do you have savings set aside in any of the following vehicles?
> account 1

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "nfe_info1", coordflippin = T) 
```

####What is your current balance?
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "balance_info_acc1", coordflippin = T) + scale_x_discrete(limits = acc_bal)
```

  + NAs?
```{r, echo=FALSE}
table(is.na(phone$balance_info_acc1))
```

\
[back to table of contents](#TOC)

#Loans 

####Do you have any loans outstanding? By loans I mean any amount money borrowed from a bank, employer, moneylender, family member or credit association.
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "l_outout_loan", coordflippin = T) 
```

####Which of the following types of loans you have outstanding?
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "l_outwhat_loan1", coordflippin = T)
```

####How many?
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "l_outlo_rep_count", coordflippin = T)
```

####What is the amount left to repay?
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "am_loan_out1", coordflippin = T) + scale_x_discrete(limits = loan_range)
```

  + NAs?
```{r, echo=FALSE}
table(is.na(phone$am_loan_out1))
```

\
[back to table of contents](#TOC)

#Remittances

####Have you made any monetary transfers to friends or family members who don't live in your household over the past 30 days either in person or indirectly?
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "rem_sentrem_s", coordflippin = T)
```

####How many different people have you transferred money to in the past 30 days?
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_hist(phone, "rem_sentn_receipients", mean = T, bin1 = F)
summary(phone$rem_sentn_receipients)
```

####How much did you send in total in the last 30 days?
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "rem_senttot_am_s", coordflippin = T) + scale_x_discrete(limits = rem_range)
```

  + NAs?
```{r, echo=FALSE}
table(is.na(phone$rem_senttot_am_s))
```

####Have you made any monetary transfers to other members of your household in the past 30 days?
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "rem_senthhtr_s", coordflippin = T) 
```

####How much have you transferred to other members of your household in the past 30 days?
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "rem_sentam_hhtr_s", coordflippin = T) + scale_x_discrete(limits = rem_range)
```

  + NAs?
```{r, echo=FALSE}
table(is.na(phone$rem_sentam_hhtr_s))
```

\
[back to table of contents](#TOC)

#Enumerator's Evaluation

####On a scale from 1 to 10 where 1 represents "did not understand at all" and 10 represents "understood perfectly" how do you judge the respondent's overall understanding of the survey questionnaire?
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=5, cache=TRUE}
plot_percent(phone, "eval", coordflippin = T) + scale_x_discrete(limits = c(1:10))
```

\
[back to table of contents](#TOC)

#Additional Analysis Requests

> Salah will get to these over the weekend.

##1) Look for possible enumerator mistakes

##2) Comparison of this data to other follow-ups (make sure it looks okay)
  + need to merge with other follow-up data

##3) Check balance of treatment groups (control, treatment1, treatment2)
  + need to merge with baseline data

\
[back to table of contents](#TOC)




